### 2020-09-04 Manuscript/What.lies.ahead.reviewed.tex
Added Fig3 captio and results of Wilcox

Likely winners under future conditions are more widely scattered among higher taxonomic groups. The haptophytes \textit{E. huxleyi} and \textit{Chrysochromulina} sp. the dinoflagellate \textit{Alexandrium sp.} each finds more suitable habitat in both of our study areas. Among others, \textit{Chaetoceros} (diatom) and {\color{red} many} hydrozoans (Cnidaria) likely increase in San Juan Island, and the potentially fish-killing heterokont flagellate \textit{Pseudochattonella} increases in {\color{red} both study areas}. See Supporting Information for a complete list of taxon-specific projections.
{\color{red}RYAN - I finished here today, will talk to you ab Wilcoxon} 
Given such heterogeneity in projections, gains and losses tend to balance one another out when looking at richness variation within phyla; we find no change in median richness for the year 2095 relative to the present in the Hood Canal(ANOVA; taxon richness  by year, p $=$ 0.7). Diatoms, however, show consistent and significant declines in richness in both Areas (Wilcoxon p $< 10^{-16}$).

@@

%%%%%
 \begin{figure*}
 \centering
 \includegraphics[width=1\linewidth]{Figures_for_MS/Top_fig3_2020-09-03.Other.sel.png}
\caption{\footnotesize{Forecasted changes in plankton in the Salish Sea. \textbf{A} Probability densities for the occurrence of individual taxa (species- and genus-level) for 2017 (blue) and 2095 (red); data are mean probabilities over 100 model draws, and variance in probability is due to differences in underlying environmental conditions. Four prominent higher-taxa are shown: Arthropods, Dinoflagellates (Dinophyceae), Diatoms (Bacillariophyta), and Haptophytes.  \textbf{B} Individual taxa with the largest changes in probabilities of occurrence between 2017 and 2095, color-coded by higher taxonomic group, for Hood Canal (left) and San Juan Island (right). Median probabilities plotted. \textbf{C} Relative taxon richness (raster color, warmer colors are more taxon-rich) for each of these same higher-taxa, for plausible ranges of pH and Temperature. Envelopes of observed (2017, blue) and modeled (2095, red) annual conditions in the Salish Sea shown for reference. Hood Canal and San Juan Island plotted separately to illustrate environmental differences between them.}}

>>>>

Likely winners under future conditions are more widely scattered among higher taxonomic groups. The haptophytes \textit{E. huxleyi} and \textit{Chrysochromulina} sp. the dinoflagellate \textit{Alexandrium sp.} each finds more suitable habitat in both of our study areas. Among others, \textit{Chaetoceros} (diatom) and {\color{red} many} hydrozoans (Cnidaria) likely increase in San Juan Island, and the potentially fish-killing heterokont flagellate \textit{Pseudochattonella} increases in {\color{red} both study areas}. See Supporting Information for a complete list of taxon-specific projections.

Given such heterogeneity in projections, gains and losses tend to balance one another out when looking at richness variation within phyla; {\color{red} we find no change in median richness for the year 2095 relative to the present in the Hood Canal(taxon richness  by year, Wilcoxon p $=$ 0.7). Diatoms, however, show consistent and significant declines in richness in that region (Wilcoxon p $< 10^{-16}$). }

@@

%%%%%
 \begin{figure*}
 \centering
 \includegraphics[width=1\linewidth]{Figures_for_MS/Top_fig3_2020-09-03.Other.sel.png}
\caption{\footnotesize{Forecasted changes in plankton in the Salish Sea {\color{red} for Dinoflagellates (panel \textbf{A}), Diatoms (\textbf{B}) and Haptophytes (\textbf{C}). Each panels shows:  (\textbf{.1}) probability densities for the occurrence of selected taxa (species- and genus-level) for 2017 (blue) and 2095 (red); data are mean probabilities over 100 model draws, and variance in probability is due to differences in underlying environmental conditions.  (\textbf{.2}) Changes in relative species richness within each phylum across the simulated scenario. (\textbf{.3}) Relative taxon richness (raster color, warmer colors are more taxon-rich) for each of these same higher-taxa, for plausible ranges of pH and Temperature. Envelopes of observed (2017, blue) and modeled (2095, red) annual conditions in the Salish Sea shown for reference. Hood Canal and San Juan Island plotted separately to illustrate environmental differences between them.}}}
